

When Declarer of suit contract does notcollects trumps or stops on the way 
and touches side  suit, that is, trump cards are on the defense side.
The principle is that declarer winners are ruffed,loosers do not be ruffed.


Because it is not done smoothly in the actual battle
Here are some examples .%and ideas

%--------------------------------------------121

\section{basic: ruffing a winner}

\qquad 2005/5/3 Yokohama BC open mem. \#14
\begin{quote}
\crdima{W/none}{%
  \begin{minipage}[t]{\br}
     4\s:\\OL:\c J
  \end{minipage}}%
  {\hand{KQ3}{K2}{A94}{AK954}}%
  {\hand{8}{A106543}{J65}{J103}}
  {\hand{J7542}{QJ9}{Q63}{Q2}}%
  {\hand{A1098}{87}{J65}{J108}}%
\end{quote}
\begin{quote}
\begin{bidding}
2\h  \> Dbl  \>P \> 2\s \\
P \> 3\h \> P \> 4\d \\
P \> 4\s \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \c J. South wins with ace. Declarer finds bad
trump break by taking \s K and \s Q. South took \c K and lead a 
club. East did not ruff it. West won with jack and 
took \h A and led a heart. Dummy won with king and led an
established club. As east was afraid of overruffing,
he did not ruff. South discarded a diamond.

South led a club again from dummy. East ruffed it and south threw an
loosing diamond(loser on loser).He made unmakable contract.

Let's count the tricks of south. 4 spades, 1 heart, 2 
diamonds and 2 clubs ,totally 9 tricks.If he wins an 
established club ,that is enough. So east must have
ruff the winner,

\vspace{0.5cm}

Next deal shows ruffing winner.\\

%-----122----------
\qquad 2005/10/21 Yokohama BC cup \#21
\begin{quote}
\crdima{S/N-S}{%
  \begin{minipage}[t]{\br}
     4\s:\\OL:\h 9
  \end{minipage}}%
  {\hand{J109}{Q1062}{QJ10}{K108}}%
  {\hand{Q43}{97}{K9842}{A93}}
  {\hand{86}{J8543}{A65}{762}}%
  {\hand{AK752}{AK}{75}{QJ54}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> - \> 1\s \\
P \>2\s \> P \> 4\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Against the opening lead \h 9, south takes
both \h A and \h K. East follows \h 5 and \h 8.
South led a small club. West won with ace at once.
After a short thinking west led \c 9. Dummy won with
king . East discarded \c2 and \c 6. \h Q was led
from dummy discarding south's diamond,

West did not ruff it, South made contract easily.
At postmotem;
\begin{enumerate}
\item{Why did west not shift to diamond?
Why did south wnat to enter to dummy? You could penetrate south's plan.
}
\item{ It was a fatal error west did not ruff \h Q.
West said his Qxx is a sure trick, He was in miss-understanding.
}
\item{
If weat ruffs \h Q by  small trump,west must lead \d 9
not \d 2. East finds the situation and returns \h J.
West's \s Q kills the contract. 
This attack is called em passant in later section.
}
\end{enumerate}
There is a famous saying:\\
leading a suit which declarercan ruff, but third hand can overruff.
\begin{flushright}{
Mike Lawrence}
\end{flushright}



 

\section{not ruffing looser}

%----------------------123---------------------
\qquad 2007/2/19 Yokohama Cup \#28
\begin{quote}
\crdima{S/N-S}{%
  \begin{minipage}[t]{\br}
     6\d\\OL:\c 8
  \end{minipage}}%
  {\hand{AK}{532}{AKQ95}{A42}}%
  {\hand{Q8}{A10987}{843}{J98}}
  {\hand{J952}{QJ64}{10}{Q1075}}%
  {\hand{107643}{K}{J762}{K63}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> -  \> P \\
P \> 2NT \> P \> 3\h \\
Dbl \>P \> P  \> ReDbl\\
P \> 3\s \> P \> 4\d \\
P \> 6\d  \>a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Let's review the bidding. When a transfer bid was doubled,
there was a choice, Pass, Redouble or 3\s. Because north has
not three supports, pass is a common one. You had better to ask
their promise. South's redouble might show a first round control,
North continues with 3\s. As shouth shows his second suit,
north did slam bid.

Opening lead is \s 8 . Dummy won. South convienced his success
upon even break of either spade or diamond suit. He saw the
bad break by \d 10 from east. He cashed \s A and \s K 
and led \h K to west. West returned \c 9. South won it with \c K.
When south led a spade , west who was a famous player in Asia, ruffed
it. Miss-defense. South can make slam along  overruff,drawing trump,spade
ruff. But south made some mistake and went to down one.

Without west's missdefense 6\d  could not be made. Don't ruff a
looser.

At another table contract was 3NT along the same bidding,
As west did not double for 3\h , the did not lead heart.
It was a west's carelessness.

\vspace{0,5cm}
Is it winner or looser?\\
 
%-------------------125----------------------------
\qquad 2007/11/23 Kanagawa Governer's cup \#27
\begin{quote}
\crdima{N/none}{%
  \begin{minipage}[t]{\br}
     2\c X\\OL:\s 3
  \end{minipage}}%
  {\hand{AK75}{Q953}{J53}{J5}}%
  {\hand{3}{AJ10}{10876}{A10832}}
  {\hand{QJ1082}{762}{AK42}{Q}}%
  {\hand{964}{K84}{Q9}{K9764}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> 1\d \> 1\s  \> 2\c \\
P \> P \>  Dbl \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \s 3. Ace wins. Small diamond from dummy.
East wins with king and leads \s Q, What does west doH
After a while,west discards a diamond, Again a diamond from 
dummy. East wins with ace  and leads \s J. west throws the
last diamond. East leads \c Q. South doed not cover it.
East leads diamond . South throws a heart. West ruffs.
West takes \h A .Finally three down,

The key point is west did not ruff the \s , Unless 
contract is down two.

In a case dummy has Axxx, west is void,
South lead a small.  Your main reading starts
not to ruff. If west ruffs, he hits nothing.


%----------------126---------------------

\vspace{0.5cm}

\qquad 2006/11/18 Koezuka Cup \#4
\begin{quote}
\crdima{N/vul:Both}{%
  \begin{minipage}[t]{\br}
     2\h X\\OL:\s A,\d J
  \end{minipage}}%
  {\hand{AK}{A107}{Q8632}{J54}}%
  {\hand{62}{K95}{J7}{AK10863}}
  {\hand{Q83}{J4}{AK10954}{Q9}}%
  {\hand{J109754}{Q8632}{-}{Q9}}%
\end{quote}
\begin{quote}
\begin{bidding}
1\c  \> 1NT! \> Dbl  \> 2\c \\
Dbl \> 2\d  \> Dbl  \> 2\h \\
Dbl \>  a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

North's 1NT overcall with 14 HCP escapes to 
2\h  doubled .
Opening lead is \c A. Esat \c 9. West shifted to
diamond. South ruffed. Accordinf to standard 
principle south cashed sidesuit first, \s A \s K.
A small club from dummy. East won with \c Q.
East led diamond. South ruffed and led \s J.

Typically a ruff in front of dummy is risky.
West ruffed by king. Dummy discarded a diamond.
Finnally contract  was double-made.

\s J is a looser. Not to ruff a looser is basic.

The case west did not ruff and discard proceeds below.
Dummy ruffs by \h 7. \c J from dummy. East discards a
diamond. Whichever south lead ,sapde or heart, he goes down.

\vspace{0.5cm}
%----------------127--------------------

\qquad 2006/12/24 Blue ribon \#11
\begin{quote}
\crdima{E/vul:N-S}{%
  \begin{minipage}[t]{\br}
     5\d\\OL:\s 7
  \end{minipage}}%
  {\hand{J}{K62}{10872}{AK986}}%
  {\hand{74}{AQ103}{Q6}{Q10532}}
  {\hand{KQ10985}{984}{43}{74}}%
  {\hand{A632}{J75}{AKJ95}{J}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> 2\s  \> 3\d \\
3\s \> 4\s  \> P  \> 5\d \\
Dbl \>  a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

South won the openping lead with \s A.
He led \c J covered by west's \c Q and dummy's \c K.
South discarded a heart under \c A. \c 9 was led from dummy.
How does east play? East thought if he does not ruff, declarer 
allows west to win with 10 leaving two winners in dummy.
So he ruffed with \d 3. To conclude earlier this is east's
mistake. Let's estimate south's pattern and winners.
Opening lead tells doubleton spade and south's four spades.
South counts at least 11 winners, including two spade ruffing tricks.
So east should discard a heart. A considerable sequence is
: South ruffs club, Ruff a spade in dummy. South ruffs club again.
South's third spade is ruffed by west's queen, West takes \h A and
leads a heart for east's ruff. South might change the sequence.

East should believe his partner, When west wins with \c 10, he surely
return a club to kill dummy's winner.

\section{reverse trump drawing}

We are talking about effective use of trump by defender.
Hereafter we talk about avoiding effective use by 
declarere .
 areverse trump  drawing is one of the effective methode.
When we were beining players, we learnt an opening lead of
trump whenever they are in miss-fit.

\qquad 2005/4/1 Yanagiya Cup \#12
\begin{quote}
\crdima{N/E-W}{%
  \begin{minipage}[t]{\br}
     5\d \\OL:\c A ,\s 4
  \end{minipage}}%
  {\hand{AK1082}{-}{82}{J98542}}%
  {\hand{J54}{8654}{9}{A10763}}
  {\hand{Q973}{Q1073}{QJ65}{Q}}%
  {\hand{6}{AKJ92}{AK10743}{K}}%
\end{quote}
\begin{quote}
Table A
\begin{bidding}
- \> 1\s \> P  \> 2\d \\
P \> 2\s \> P \> 3\h \\
P \> 4\c \> P \> 4\h \\
5\d \>a.p.
\end{bidding}
\end{quote}
\begin{quote}
Table B
\begin{bidding}
- \> P \> P  \> 1\d \\
P \> 1\s \> P \> 2\h \\
P \> 3\c \> P \> 3\h \\
P \> 4\c \> P  \> 4\d\\
P \> 5\d \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

In both table they did not have fitting suit  and
reached to 5\d which is miss-fitting.

Without cashing \c A, dummy's solid spade discards,
Both west took \c A and led \s 4. A declarer made
contract by leadinf \c J. Declarer of out team failed
There exists clear difference in south's play.

To conclue earlier if west leads a trump ,the cont
will go dowm. Stupid west explained at postmotem
that singleton tump lead  will kill an hornour of
east.  Reverse drawinf gains a trick, It never loss
totally.

Agaist the secont rick of \s 4, high level player
wins ace and lead \c J. Ther are a lot of variaion 
branches but if southplays correcyly he can make
contract,

Without hesitation second trick must br a a trump.

\vspace{0.5cm}

When we do find ourselves defending against the opponents' 
two suiters, it is usually right to lead trumps. Declarer rates to be short
in dummy's second suit, so tend to lead a trump.- even from a non-ideal holding.\begin{flushright}
{ Marty Bergen}
\end{flushright}


%----------------------130----------------------

\qquad 2007/2/21 Yokohama Cup \#29

\begin{quote}
\crdima{S/Both}{%
  \begin{minipage}[t]{\br}
     1\d X\\OL: \s Q
  \end{minipage}}%
  {\hand{J954}{1097}{54}{9743}}%
  {\hand{Q}{Q632}{QJ763}{AJ8}}
  {\hand{K1062}{AKJ8}{102}{Q106}}%
  {\hand{A873}{54}{AK98}{K52}}%
\end{quote}
\begin{quote}
Table A
\begin{bidding}
- \> - \> - \> 1\d \\
P \> P \> Dbl \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\


%------------131---------------------------
When a takeout-double is treated as a pelty, a lead of trump is 
effective in order to be inactive for small ones.

West's opening lead is \s Q.  South wins with ace.Small heart from dummy.
East wins with jack. He willinglly continues top hearts. South ruffd with \d 8.
Later south's \d 9 won. Two down -599 points.

East should have lead a trump when he won with \h J.
As west is sitting behinf south , he is difficult to lead trump.
So east must do as earlier as possible,

At the bidding it is usual that north bids redouble in stead of
his last pass in order to escape.

At another table E-W obtained 3NT saving less damege.

% low contract is doubled

When declare holds a two-suiter and opening leader has length and strength in non-trump suit, a trump lead is indicated.
Two other common situationscall for a trump lead:\\
a) when you are defending a low level doubledc contract\\
b) when your side holds the great majority oh HCP.

\begin{flushright}
{ Augle Boehm:\\
Bridge Snarts\\
A Path to Bridge Success}
\end{flushright}


\vspace{0.5cm}
Drawing trump by defender is effective

\qquad 2007/2/21 Yokohama Cup \#30
\begin{quote}
\crdima{E/vul:none}{%
  \begin{minipage}[t]{\br}
     3\h \\OL:\s K
  \end{minipage}}%
  {\hand{5}{KQ1097}{J10642}{653}}%
  {\hand{KQ972}{-}{A98}{KJ974}}
  {\hand{1064}{J7543}{K7}{A108}}%
  {\hand{AJ83}{A862}{Q53}{Q2}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> P \> 1\c \\
1\s \> Dbl \> 2\s \> 3\h \\
 a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\
%--------------------132-------------------

This deal apperaed inthe Yokohama cup(old NEC) elimination
final round. Opponent 0s Korea.

1\s is conatructive with support. Some pair reaches at 4\s and
went down. Our team mate lost -300 by four heart dobled two down.
In our table we defend three heart.

Opening lead is \s K. South wins with ace. South draws trump once revealing
5-0 break. A small diamond from dummy. East went up with \d K and led a
trump. Finally contract was down three, Differnce is two tricks.
How effective the reverse drawing is !


\vspace{0.5cm} 
An overtake is required.\\

\qquad 2007/7/21 Montalt Cup \#30
\begin{quote}
\crdima{S/vul:None}{%
  \begin{minipage}[t]{\br}
     4\s :\\OL:\s 5
  \end{minipage}}%
  {\hand{A74}{63}{J764}{AQ92}}%
  {\hand{10865}{AJ108}{K2}{J108}}
  {\hand{9}{KQ42}{Q10985}{654}}%
  {\hand{KQJ32}{975}{A3}{K73}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> -  \> 1\s \\
P \> 1NT \> P \> 2\c \\
P \> 4\s \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is a trump.South leads a heart. West wins and leads a trump again.
Dummy leads a heart. East plays \h Q. South \h 5. West overtakes with \h A
and third trump. At this stage the location of \h K was unknown, South
planed a chance for club 4-2, But actually club was 3-3 break. 
West's effort was not rewarded , making four.



%--------------------133-------------------
\section {basic trump promotion}
\qquad 2007/5/31 Yokohama sectional \#30
\begin{quote}
\crdima{N/vul:None}{%
  \begin{minipage}[t]{\br}
     4\h :\\OL:\s A
  \end{minipage}}%
  {\hand{75}{KQJ}{AK98}{KQ42}}%
  {\hand{AK1086}{105}{Q103}{1086}}
  {\hand{43}{A96}{7654}{J953}}%
  {\hand{QJ92}{87432}{J2}{A7}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> 1\c \> P  \> 1\h \\
P \>3\h \> P \> 4\h \\
1\s \>Dbl \> P  \> 2\h \\
P \> 4\h \>a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \s A.
West shifted yo \h 5. East won with ace and returned \s 3.
West won and led small spade. Dummy ruffed. East's 9 promoted.
Defender took two tricks in each major.

Ta anothe table they made 3NT. 
%----------------------page 134-------------------
\vspace{0.5cm}
Next deal shows refusing overruff.\\

\qquad 2004/9/30 Yokohama sectional \#9
\begin{quote}
\crdima{N/vul:E-W}{%
  \begin{minipage}[t]{\br}
     2\h :\\OL:\d 8
  \end{minipage}}%
  {\hand{KQ}{432}{A62}{KQ1072}}%
  {\hand{J108653}{KJ76}{83}{5}}
  {\hand{97}{8}{KQ1074}{AJ643}}%
  {\hand{A42}{AQ1095}{J95}{98}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> P  \> P \\
P \> 1\c \> 1\d \> 1\h \\
P \> 2\c \> P  \> 2\d \\
P \> 2\h \>a.p.
\end{bidding}
\end{quote}

Opening lead is \d 8. Dummy small. East wins with queen.
He returns \h 8. Soutj \h 0. West wins with jack.
West leads \d s again. Dummy is ace. South unblocks \s K and \s Q.
Come back to the hand with \h A and discards \d 6 under \s A.
\d J from hand. West discards a club.Dummy ruffs. \c K from dummy.
East wins with \c A. He leads \d K. South ruffs with \h Q.
West made a mistake to overruff with \h K. They made three.
Unless he overruffed,
defender wins two tricks in trump. He was overlooked at \h 8.
They made two.

East was more kind to return club in stead of \d K noy to cause a 
mistake.


%------------------------135--------------------
\vspace{0.5cm}

Next deal shows refuding a ruff.\\

\qquad 2006/1/14 Japan league \#10
\begin{quote}
\crdima{S/vul:Both}{%
  \begin{minipage}[t]{\br}
     4\h :\\OL:\c K
  \end{minipage}}%
  {\hand{862}{KJ82}{AQJ96}{5}}%
  {\hand{J1053}{5}{K4}{KQJ862}}
  {\hand{AKQ7}{A73}{108753}{7}}%
  {\hand{84}{Q10964}{2}{A10943}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> -  \> P \\
3\c \> 3\d \> P  \> 3\h \\
P \> 4\h \>a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \c K.  South wins with \c A.
He cashes \d A and \d Q discarding \s 4. West wins with \d K.
West led \c Q. Dummy ruffed by \h J and eas overruffed by ace.
South made contract with shamed defense.
Of course if east did not overruff ,contract was defeated.
He lost trump cotrol for the entry to dummy who has a
plenty established diamond.
East confessed his overruff is acused. Another mistake is 
weest's \c Q. He should have lead spade. A mistake might
cause apartner's mistake.

Opening 3\c bid is not a compliment. They can fight
up to three spades.
During defense , communication mind with mind is ideal.


%--------------136---------------------
\section{uppercut which side}
\qquad 2008/6/30 Yokohama sectional \#15
\begin{quote}
\crdima{S/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\s :\\OL:\d J
  \end{minipage}}%
  {\hand{A10987}{42}{A6532}{J}}%
  {\hand{J65}{K8765}{J109}{84}}
  {\hand{Q3}{AJ3}{K74}{97632}}%
  {\hand{K42}{Q109}{Q8}{AKQ105}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> -  \> 1NT \\
P \> 2\h \> P \> 2\s \\
P \> 4\s \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Contract and opening lead were same at boyh tables.
Difference happens on the fourth trick. along south \d A,
\c J to \c A, \c K discards a heart and south leads \c Q.

In a table west ruffed by \s 5 anf at another table 
by \s J. \s 5 is Obvious mistake thay making four.
 
Dummy overruffed by \s A.
Contract was defeated, Originally declarer has a 
loose in trump. But rufiing by \s 6 lost the trick.
rufiing by \s J remains a looser unless declarer
\index{uppercut}
performed spade finess. This ruffing is called as uppercut.
By uppercut  partner's trump might promote.

To adding conclution, south can make contract if he
discards a heart when west did uppercut.




%--------------137---------------------
\section{coup  en passant}

\qquad 2007/7/13 Yotsuya league \#17
\begin{quote}
\crdima{E/vul:none}{%
  \begin{minipage}[t]{\br}
     3\d :\\OL:\c 5
  \end{minipage}}%
  {\hand{A1084}{QJ1073}{Q3}{Q2}}%
  {\hand{6532}{K6}{J1072}{K75}}
  {\hand{KQJ}{A952}{9}{J8643}}%
  {\hand{97}{84}{AK8654}{A109}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> 1\c  \> 1\d \\
1\s  \> 2\h \> Dbl \> 3\d \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Against opening lead \c 5, dummy's good judge plays \c Q. Then  \c A
cashed, The third roung of club was ruffed. Defenders were impatient.

South drew trumo once by \d Q and cashed \s A then led \s 4.
East won with queen and led \c 8. South ruffed with \c 5 and
west overruffed. by \c 7. West led \h K and small . East won with ace
and led \c J . South ruffed with \d K. Due to bad break of trump
contract went down one.

Although opening lead was wrong, defenders coup recoverd the game.
If south did not ruff \c 8 discarding heart, he could make contract,
Tahai is looser on looser.
%--------------138---------------------

\vspace{0.5cm}

\qquad 2007/8/10 Iwasa Cup \#6
\begin{quote}
\crdima{E/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\c :\\OL:\s 6
  \end{minipage}}%
  {\hand{J1084}{J962}{AK}{K85}}%
  {\hand{62}{K83}{QJ753}{J94}}
  {\hand{AK973}{AQ1074}{96}{7}}%
  {\hand{Q5}{5}{10842}{AQ10632}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> 1\s  \> 3\c \\
P  \> P \> 3\h \> P \\
P \> 4\c \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Oening lead is \s 6.East took his king and ace. He was temted to
take \h A, but he returned \s 9. He has a plan of two down along below:
West ruffs spade. Come back with \h A . West ruffs spade.
But at the third round of spade, south threw a samll heart.
West returned aheart but south ruffed. He collected trumps
and make contract.
South explained the circumstance at key point.
There was a fact west chose heart other than spade in bidding.
This implies south's spade is short.

\index{coup em passant}
If east cashed \h A in advance,	 A typical coup em passant
became a winning shot.
%--------------139------------------

\qquad 2004/9/10 Yotsuya \#10
\begin{quote}
\crdima{W/vul:Both}{%
  \begin{minipage}[t]{\br}
     4\s X:\\OL:\d A ,\s 7
  \end{minipage}}%
  {\hand{J10832}{AQ862}{74}{6}}%
  {\hand{7}{KJ107}{AK10}{AQJ93}}
  {\hand{964}{95}{J82}{108542}}%
  {\hand{AKQ5}{43}{Q9653}{K7}}%
\end{quote}
\begin{quote}
\begin{bidding}
1\c  \> 2\c \> P  \> 4\s \\
Dbl \> a.p.
\end{bidding}
\end{quote}
%------------140------------
\vspace{0.5cm}
Next deal anoies discarding.\\
\qquad 2005/10/10 Yotsuya
\begin{quote}
\crdima{N/vul:none}{%
  \begin{minipage}[t]{\br}
     3\s :\\OL:\h x(3 rd low)
  \end{minipage}}%
  {\hand{AQ10}{10xxx}{AK10x}{xx}}%
  {\hand{Jx}{xxx}{Qxx}{Axxxx}}
  {\hand{K9xx}{xxx}{Jx}{KQxx}}%
  {\hand{8xxx}{AKQ}{98xx}{Jx}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> 1\d \> P  \> 1\s \\
P \> 2\s \> P \> 3\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\



Opening lead is \d A. Weat leads \s 7. South wis with A.
South took heart finess with \h Q and \h A. He trumped third
heart with \s K. A low spade to dummy's jack. East had sent
trump echo with \s 6 then \s 4. South ruffed fourth heart 
with \s Q. South wants to enter to dummy in order to draw
remaing trump. A small diamond from hand. West played 10.
East overtook with jack. East returned a club. West ace was
last trick. Decleare made doubled contract.

East made mistakes upon discarding.
If he threw two diamonds under the heart,
west's diaamond return can promote \s 9. Of course
\c A must be cashed in advance.
Defenders must consider explicantlly.
 

%-----------141---------------
\section{promotion and control}


\qquad 2006/11/18 Koezuka Cup \#14
\begin{quote}
\crdima{S/vul:none}{%
  \begin{minipage}[t]{\br}
     4\s :\\OL:\d 8(3 rd low)
  \end{minipage}}%
  {\hand{KQ87}{J76}{543}{KQ9}}%
  {\hand{9}{Q983}{Q1082}{A643}}
  {\hand{10543}{42}{AJ9}{J752}}%
  {\hand{AJ62}{AK105}{K76}{108}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> -  \> 1NT \\
P \> 2\c \> P \> 2\h \\
P \> 3NT \> P \> 4\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \d 8 (3rd low). East wins with ace and returned a
diamond. South drew two rounds of trumps revealing bad break.
A small club from hand. Dummy's king won.South did heart finesse
which failed into west's \h Q. West cashed \d Q. At this point
west returned heart so he got only one down,

If west retured 13 th diamond after he cashed \c A,
partner's trump will  promote whoever ruffs it.


When you are looking for an uppercut or trumo promotion, consider
whether you have to take your ither winners first.\\
\begin{flushright}
{Mike Lawrence}
\end{flushright}




-----------142---------------


\qquad 2004/9/18 Takamatsu memorial Cup \#2
\begin{quote}
\crdima{S/vul:E-W}{%
  \begin{minipage}[t]{\br}
     3\d :\\OL:\d x
  \end{minipage}}%
  {\hand{xxx}{10}{Qxx}{AQJxxx}}%
  {\hand{AQJxx}{xxx}{9xx}{Kx}}
  {\hand{Kxx}{Axxx}{108x}{xxx}}%
  {\hand{xx}{KQJxx}{AKJx}{10x}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> -  \> 1\h \\
1\s \> 2\c \> 2\s \> P \\
P \> 3\c \> P \> 3\d \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

South wins diamond opening lead with \d J. A samll
heart to 10 was taken by east's ace. Three rounds of spades were
played. South did not ruff discarding a club whchi might be
a looser. It seems the contract is safe. But curious west led
4 th spade, As cards lie ,if south ruffs with qeen anf believes
3-3 break he can make contract. But he ruffed with dummy's low trump.
East overuffed with \d 8. South  ruffs with king. Due to blocking of \d Q
south can not draw trumps. So he played \c A ,\d Q, \c Q and \c J.
West ruffed and contract went down one. Against 4-2 break, south executed safetyplay. But a forcinf defense along ruff and discard defeated contract.

At another table, north's 3\c is made four, getting 4 IMP.

%-----------143---------------
\vspace{0.5cm}

\qquad 2007/2/19 Yokohama Cup \#24
\begin{quote}
\crdima{S/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\s :\\OL:\d A
  \end{minipage}}%
  {\hand{K986}{J}{K93}{107654}}%
  {\hand{2}{Q76}{A10872}{AQ83}}
  {\hand{10543}{K102}{QJ65}{92}}%
  {\hand{AQJ7}{A98543}{4}{KJ}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> -  \> 1\h \\
2\d \> Dbl \> 3\d \> 3\s \\
P \> 4\s \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

This deal was introduced in the bulletine of the ournament. They reported
a failure and success.

At a table,opening lead is \d A and a diamond was continued, South ruffed in thehand(commented as a curious). South cashed \h A and ruffed a heart in dummy.
A low club from dummy. West wins both ace and queen and led third diamond.
Dummy's king won. Declarer led \c 10. East did not ruff and discarded a
winner \h K! South came back with trump and ruffed a heart with high trump.
He can not catch east's trump.

We have talked about ruffing a winner. But in this deal our problem is
to keep conrol. South wanted a line of cross-ruff but he he lost contol
by shortening trump. On the contrary east kept control by discarding winner.

At another table, opening lead is \d A, West led a diamond and dummy
won with king. Small club from dummy. West won with \c Q and led a
diamond \. South ruffed and exit with \c K.
West won. But he madea fatal mistke by leading \c 8. West was feard about
leading red suits, South made contract along cross-ruff style.

Although west refused to lead red suit, any red suit can be defeated.
When west led a diamond ,it might gave ruff and sluff. But the lost control.
Sush a defense is called as forcing defense we wiil talk in next chapter.


%-----------145---------------

{\bf mission impossible side-suit}

\qquad 2004/7/30 Montalt Cup \#21
\begin{quote}
\crdima{S/vul:N-S}{%
  \begin{minipage}[t]{\br}
     4\h :\\OL:\h 3
  \end{minipage}}%
  {\hand{K96}{985}{Q2}{KJ1093}}%
  {\hand{A107}{K643}{KJ1064}{A}}
  {\hand{Q85432}{J}{853}{842}}%
  {\hand{J}{AQ1072}{A97}{Q765}}%
\end{quote}
\begin{quote}
\begin{bidding}
-  \> - \> -  \> 1\h \\
2\d \> 2\h \> P \> 4\h \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\
\index{pump}
Opening lead is \h 3. East plays \h J. South wins with \h Q.
South leads \s J .East low. Dummy \s K wins.  South led \d Q  which
west won with king. \s A was ruffed. South cashed \d A anf ruffed 
a diamond. trump from dummy. East showed out. West won with king.
West's diamond pumped south. Finally three down.If west wins \s A 
at trick two, contract can not be defeated, Second low is a point.
South believed \h K in east. A trump lead from Kxxx or Kxx is done
frequently. 

The biggest mistake of declarer is not  to lead club, He should 
establish his side suit.




