During developing bridge, we learn to lose the tricks.
It appears on holding, to lose twice or three for establising, 
To rectifing for squeeze. Hold, not to hurry to win, is very
important but is not fully understood,

\section{not to win is a choice}
\qquad 2007/9/29 Hagiwara Cup \#9
\begin{quote}
\crdima{S/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\s:\\OL:\s 4
  \end{minipage}}%
  {\hand{A543}{A4}{863}{A975}}%
  {\hand{102}{KJ10}{KQ5}{KJ862}}
  {\hand{98}{98653}{A109}{11043}}%
  {\hand{KQJ76}{Q72}{J742}{Q}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> - \> 1\s \\
P \> 3NT \> P \> 4\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \c 2. North's ace wins, South's \s K collects trumps.
South leads a small diamond. West wins with \d Q without thinking.
West leads \c K which is reuffed by south. South leads a diamond 
again. West wins with \d K and leads a club.

South ruffs and leads third diamond to east's ace,
East shifted to heart but it was too late, 13th diamond 
was able to discard dummy's heart.

West was acused why he hurried to win \d Q. If he
played a small, east could lead a heart. If dummy's heart was 
Jxx (or 10xx) ,queen might be considerable. Second hand low is a
basic principle.

This hand is not so difficult, At another table, west repeated 
three times of diamonds. South made four.
 After \d K , small diamond to \d A. 
If east returns heart, defense succeeds, But as east might
think west was doubleton king, he might play diamond.

\vspace{0,5cm}

"Second hand low" with negative inference.\\


%------------------58------------------------
\qquad 2008/6/30 Yokohama sectional \#27
\begin{quote}
\crdima{S/vul:none}{%
  \begin{minipage}[t]{\br}
     5\d:\\OL:\h 2
  \end{minipage}}%
  {\hand{Q}{A3}{A1062}{KJ9765}}%
  {\hand{K63}{J72}{Q843}{Q32}}
  {\hand{10985}{K9854}{-}{A1084}}%
  {\hand{AJ742}{Q106}{KJ975}{-}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\s \\
P \> 2\c \> P \> 2\d \\
P \> 3\d \> P \> 5\d\\
a.p.
\end{bidding}
\end{quote}

{\bf Remarks}\\
In the both tables, contract and OL are same. At our table.
east wins with king and shifts to \s 5, \s A wins. South draws
trumps by ace.East showed out. From dummy \c 5 is led.

East played ace!! South ruffed. A spade wsa ruffed in dummy.
Cashed \h A and \c K discardind a spade.South ruffed a club.
South cashed \h Q, spade ruff, Dummuy les \c J discarding
a winner \s J, West was thrown-in. He gave two trick 
to ward \d K and \d J.

Why east played \c A at once. The clue is tha fact 
if south had a club, he would have lead from hand toward
king and jack. If south had a singleton \c Q, he would
plan to establish club or could have tried to  bid 3NT.
Such a idea is called "negative inference".

The Official Encyclopedea of Bridge explains:
Imformation deduced from a plyer's falure to take a
specific actionin the bidding or play. Though this type of inference is 
frequently avaiable, if it is often overlooked. The average player
 prefering to concentrate on motr positive clues.

At another table \h A won on opening lead, A small club from dummy 
invited east's ace. This is a sole chance to make contract.

%------------------57----------------------
\vspace{0.5cm}
routine not to win at once! one of a basic pattern.\\

\qquad 2006/9/15 Takamatu Cup \#28
\begin{quote}
\crdima{N/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\h \\OL:\c 6
  \end{minipage}}%
  {\hand{Kx}{Axxx}{KQ8x}{Q8x}}%
  {\hand{AQJxx}{Qx}{Jxx}{962}}%
  {\hand{xxxxx}{Jx}{Axx}{K107}}
  {\hand{10}{Kxxxx}{109x}{AJ43}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> 1\d  \> P \> 1\h \\
P \> 3\h \> P \> 4\h\\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

\index{MUD}
Opening lead is \c 6 according to MUD. Dummy \c Q, east\c K and
south wins with \c A. After drawing trumps twice, south leads \d 10.
West small. Dummy's king wins.( Easr ducked smoothly.) Declarer
believes \d A in west.

He came back to his hand with trump. He leads the diamond again.
West small. Dummy \d Q. East wins with ace. Down one.

Following position gives resemble play.\\
\qquad \qquad KQ10\\
\qquad xxx \qquad AJx \\
\qquad \qquad xxx\\
Small card from south. North king, East ducks without hesitation.
Be sure such a custom. Even when 10 is missing, once duck is prefered.


%------------------58------------------
\vspace {0.5cm}
K and Q are separated ,typical pattern appeared frequently.\\

\qquad 2007/11/4 Studio \#13
\begin{quote}
\crdima{N/vul:Both}{%
  \begin{minipage}[t]{\br}
     3NT:\\OL:\c 2
  \end{minipage}}%
  {\hand{QJ7}{Q82}{Q87}{KJ92}}%
  {\hand{K9654}{43}{J65}{1043}}
  {\hand{82}{KJ975}{A43}{865}}%
  {\hand{A103}{A106}{K1092}{AQ7}}%
\end{quote}
\begin{quote}
\begin{bidding}
P \> P  \> 2\h  \> 2NT\\
P \>  3NT \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \h 4. Dummy small. East \h J. South wins with ace
without ducking. Then he leads \d 2. Dummy's \d Q wins.
Since this game is under IMP \& SRR, an overtrick is valuable.
From dummy \d 7 was led followed by \d 4, \d 10 and \d J.

After a short thinking west led \h 3. East won with king and retured the 
third heart. South won. After south took four club tricks ,he planed
a throw-in into west's ace. Alas diamond ace appeared from east.
This is a typical example not to take with ace.
(\d A should be reserved for an entry when west has doubleton in heart.)

A mention should be added, South should have held the first trick.
Even if he has double stoppers, ducking is a basic play.
When he won with \d Q, he had better to develope spade suit.
Even if the finesse failed, he counts up 9 tricks
(\s 2,\h 2, \d 1,\c 4). 

South's hangry spirit coursed two miss playing.

%-------------59-------------------------
\vspace {0.5cm}

K behind AQJ,typical pattern appeared frequently.\\
\qquad 2007/11/4 Studio \#23
\begin{quote}
\crdima{N/vul:Both}{%
  \begin{minipage}[t]{\br}
     4\s:\\OL:\h 5
  \end{minipage}}%
  {\hand{J975}{743}{AQJ}{KQ2}}%
  {\hand{62}{K105}{1063}{A9873}}
  {\hand{K10}{QJ96}{K9872}{54}}%
  {\hand{AQ843}{A82}{54}{J106}}%
\end{quote}
{\bf Remarks}\\

Opening lead is \h 5 ,third best. East plays \h J.
South ducks. South wins next heart and leads a diamond to 
dummy's jack. East ducks smoothly.
East awares south has anothe loser in heart.
Since \c A is not found yet, his \d K is not enough to set
contract.

South transfered to hand by \s A without to do finesse.
he performed diamond finesse again. He lost the chance to
finesse spade.

Those not in hurry get something. The king behind
AQJ is worth to discuss.


%-------------60-------------------------
\vspace {0.5cm}

\section{second hand low by count the trick}
second hand low by counting tricks\\
\qquad 2005/12/6 Yotsuya  \#32
\begin{quote}
\crdima{W/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\h :\\OL:\c A
  \end{minipage}}%
  {\hand{A}{A9863}{KQJ96}{J2}}%
  {\hand{2}{-}{A8532}{AKQ9764}}
  {\hand{KJ10865}{J752}{74}{8}}%
  {\hand{Q9743}{KQ102}{10}{1053}}%
\end{quote}
\begin{quote}
\begin{bidding}
1\c \> 2NT  \> P \> 3\h \\
P \> 4\h \>  a.p.
\end{bidding}
\end{quote}

\begin{quote}
\begin{bidding}
1\c \> 1\h  \> P \> 3\h \\
4\c \> 4\d \> P \> 4\h \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

At the beginning west continued three top clubs.
Declarer ruffed with \h A. East discarded two diamonds.
Declarer led \h 3 from dummy to \h K, revealing bad break.
South led \d 10, West knows it is a sigleton,

To conclude earlier, west must not take it. Be sure east can 
ruff the diamond.

Since east had four trumps( \h 2 followed), south can ruff
dummy's losindg diamond only three times. Even if west took ace,
a next winner is not secure. If west took ace, all the diamonds
are winners.

Thit is a high level hand. But it seems to be at an extension of
standard pattern.

As soon as the game is over,the professor told that unless west played
\d A, defense was in succsess.

At another table  north is declarer. East leads \c 8.
West played \c Q \c K  \d A( questionable) and \c A.
North ruffed by \h 9, overruffed by \h J. 
%--------------------61------------------
\vspace{0.5cm}
Next deal shows not to increase tricks with low in both second and third
hand,\\
\qquad 2005/2/9 NEC cup  \#8
\begin{quote}
\crdima{W /vul:none}{%
  \begin{minipage}[t]{\br}
     4\h :\\OL:\s 8
  \end{minipage}}%
  {\hand{64}{A9853}{J75}{K94}}%
  {\hand{87}{J1072}{10964}{865}}
  {\hand{A10932}{-}{KQ3}{AJ1032}}%
  {\hand{KQJ5}{KQ84}{A82}{Q7}}%
\end{quote}
\begin{quote}
\begin{bidding}
P \> P  \> 1\c  \> 1NT \\
P \> 2\d \> 2\s \> 3\h \\
P \> 4\h \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

East played \s A simply, and returned a spade.
Declarer made easily. The owner of \s KQJ is evident.

East could deduced partner was not 
singleton. Otherwise south's five card spade altered the
bidding. East should play small.

After collecting a trump, south leads a  second spade from dummy. 
East put up with \s 9. Declarer is lack of tricks.

Those not in hurry perfom winning defense.

Another plan to defense is that to shift diamond after
winning first trick with ace, expecting a trump and \d 10 in west.


%--------------------62------------------
\vspace{0.5cm}
Next deal shows a routine not to win made big loss.\\
\qquad 2007/8/10 Iwasa cup  \#12
\begin{quote}
\crdima{W /vul:N-S}{%
  \begin{minipage}[t]{\br}
     3NT :\\OL:\h J
  \end{minipage}}%
  {\hand{Q8}{102}{AQ9}{A107632}}%
  {\hand{K6}{J4}{J108764}{J85}}
  {\hand{AJ74}{Q9653}{2}{K94}}%
  {\hand{109532}{AK87}{K53}{Q}}%
\end{quote}
\begin{quote}
\begin{bidding}
P \> 1\c  \> 1\h  \> 1\s \\
P \> 2\c \> P \> 2NT \\
P \> 3NT \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\


South won the opening lead with ace, \c Q is led to west.
Stupid west, who has learnt not to take hurry, ducked it
smoothly. Declarer was told clubs devided even 3-3.
When dummu has few entries, holding might has a some
effect. Dummy has two entries whoever has \d K.

Don't duck without analize.

%----------------------63------------------
\vspace{0.5cm}
Cover an honour with an honour\\
\qquad 2007/2/19 Yokohama Cup \#1
\begin{quote}
\crdima{S/vul:none}{%
  \begin{minipage}[t]{\br}
     4\s :\\OL:\d 4
  \end{minipage}}%
  {\hand{5}{QJ85}{K73}{KJ1062}}%
  {\hand{J642}{K62}{Q964}{43}}
  {\hand{K3}{1073}{A82}{Q9875}}%
  {\hand{AQ10987}{A94}{J105}{A}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\s \\
P \> 1NT \> P \> 3\s \\
P \> 4\s \>  a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Since 2019 NEC cup changed its name to Yokohama cup.
It is always a lively competition, This deal appeared
in a game against England team who has experieced to win
victory in 2017.

Against the opening lead, south in thinking for a while.
East also do and  regards as fourth best ,
and plays smoothly \d 8 over dummy's \d 3.

It neglects the rule "third high" but he thought \d A can take
anytime later. Another fact that during lead in south ,
south can not do spade finess.

South unblocked \c A . took \s A and led \s Q. 
East won with \s K and returned \h 7. West's \h K went down one.

At another table 3NT by north is made, giving 10 IMP score.

\section{promotion has winning effect}
Promotion is an unfamiliar word. Simple example ;
South leads queen. Dummy has ace. you west cover the queen with your
king. The king is lost. But jack becomes champion whoever holds it.

"Cover an honour with an honour" leads to promotion.

The first one is a simple example:\\


\qquad 2004/3/13 Studio  \#17
\begin{quote}
\crdima{vul:none}{%
  \begin{minipage}[t]{\br}
     6\c :\\OL: \s K
  \end{minipage}}%
  {\hand{6}{K974}{A7}{AK8643}}%
  {\hand{AK10742}{653}{K92}{J1J}}
  {\hand{Q98}{J102}{J8532}{72}}%
  {\hand{J53}{AQ8}{Q106}{Q1095}}%
\end{quote}
{\bf Remarks}\\

\index{chineese finesse}
Bidding unknown. After cashing \s K, west led \c J.
Declarer drew trumps twice and led \d Q from hand.
West did not cover with \d K. He neglected the
saying "Cover an honour with an honour".
He owns unmakable slam. This finess called chineese
finess\footnote{
In bridge, a Chinese finesse is a "pseudo", or fake, finesse.
}. He fas no excuse for team mates.


Another example of chineese finess.\\
After the bidding 1\s - X - 4\s -5\h , dummy opened :\\
\qquad \qquad \h A9652\\
West , having \h K4,  annoies against \h Q from south.
If south has five card trumps, south might play dropping king.
West decided not to cover. Actually \h Q won.  East small. 
It was a astonishment when east dropped \h J on second trick.
South bids 5\h with only four cards and did chineese finess.
In such an unlucky day , my game never win.

\vspace{0.5cm}
In next deal, honest cover is suitable.\\
%-------------------65----------------
\qquad 2006/10/27 Yotsuya  
\begin{quote}
\crdima{vul:none}{%
  \begin{minipage}[t]{\br}
     3NT:\\OL:\c 4
  \end{minipage}}%
  {\hand{QJ98}{AJ5}{K92}{J82}}%
  {\hand{A10765}{98}{Q8}{Q1074}}
  {\hand{3}{432}{AJ1054}{K963}}%
  {\hand{K42}{KQ1076}{763}{A5}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\h \\
P \> 1\s \> P \> 1NT\\
P \>  3NT \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\


Opening lead seems fourth best. Dummy \c 2. How does east
play? According to the saying about an honour , \c 8 is
honest. Easy could not affirm the four best, doubting three cards.
West might hold the ace. East was blinded by his diamonds.
So he played king. South ace won. At this point east was
optimistic even though he guessed wrong. He expected diamond return.

South led \s 2 from hand and dummys queen won. Small spade from 
dummy . East discarded \c 3 just in case.

West won south's king with ace. East wanted to shift to diamond eagerly 
but west led \c Q  and another club. 3NT completed.
West might be tired during two days fighting. 

He should think why south wants to produce spade winners without
touching his heart suit. \c J8 behind \c Q is a threat for west.

At another table openind lead is same, As east played \c 9,
contract failed.


Some examples below show the third hand pkay
assuming fouth best in NT contract:

\begin{enumerate}
\item {
\qquad 10xx\\
\qquad \qquad AJx \qquad 
\begin{minipage}[t]{\br}
Ace wins Return x is best noy J .
\end {minipage}
}
\item {
\qquad 10xxx\\
\qquad \qquad AQ9 \qquad 
\begin{minipage}[t]{\br}
Play small when dummy small.
\end {minipage}

}
\item {
\qquad Q5 \\
K832 \qquad A86 \qquad 
\begin{minipage}[t]{\br}
This is also snall 8.
Defender can get three tricks.
\end {minipage}\\
\qquad J1074 
}


\end{enumerate}

\section{Not to hurry on opening lead 
blesses you}


%-----------------68-----------------
\vspace{0.5cm}
\qquad 2006/5/20 Yokohama sectional \#24
\begin{quote}
\crdima{S/vul:none}{%
  \begin{minipage}[t]{\br}
     6\d \\OL:\h A
  \end{minipage}}%
  {\hand{J8}{Q10}{KJ1098}{AKQJ}}%
  {\hand{Q954}{A876}{42}{543}}
  {\hand{K1064}{J942}{73}{1075}}%
  {\hand{A32}{K53}{AQ62}{982}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\d \\
P \> 2\d \> P \> 2NT\\
P \> 3\c \> P \> 3\s \\
P \> 4NT \> P \> 5\s \\
P \> 6\d \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

After west heard the bidding, he cased \h A. This is the only lead slam
can be made. West told the heart is un-bidden suit so A and K are expected.

After the game N and S explainded their bidding system.
2NT garenteed stoppers in major suits. 3\s does not imply ace. Italian cue 
bid is not used. So cue bid with king is not called. Therefore north convienced
\h K in south. He went to slam by using 
RKCB\footnote{
Roman Key Card Blackwood is a variation of the Blackwood convention. It is used when the partnership has agreed to a trump suit and is interested in slam. A 4NT bid asks partner how many "key cards" he holds. A key card is any ace or the trump suit king.
}.

Above explanation should be heard before opening lead. A active lead is
\s J while a passive lead is \d 4.

{\bf closing intermission}\\
%---------------68-9---------------
\begin{description}
\item[no 1]{
Generally many beginners like to lead an ace in opening lead 
against slam. They dislikes an under-lead from king. The reason
of bad ace is to give two winners at once. The loss of king is
only one. Moreover slam side has much HCP than that of defender.
An under-lead from king expects  2 HCP of queen in 
his partner. Whereas the ace expects 4 HCP of king. From the
probability the queen is ahead to the king. From the both 
point of view, more under-lead from king should be tried.
Nevertheless to hear the bidding is important. 

}
\item[no 2]{
There is a case cashing an ace is necessary.
Otherwise declarer can vanish a looser under the
solid side suit. You should learn these cases 
from their bidding, For example dummy has solid side
suit.

}
\item[no 3]{
High level players develop good result, 
When good result is in coincidental, the result
differs from that of good players,

}
\end{description}

%-------------70-------------
\vspace{0.5cm}
\qquad 2007/2/19 Yokohama Cup  \#3
\begin{quote}
\crdima{N/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\s \\OL:\s 8 or \d A
  \end{minipage}}%
  {\hand{AJ5}{AK8652}{3}{KJ3}}%
  {\hand{K943}{-}{AJ105}{Q8764}}
  {\hand{10}{GJ10973}{98642}{10}}%
  {\hand{Q8762}{4}{KQ7}{A952}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> 1\h  \> P \> 1\s \\
Dbl  \> ReD \> 2\d  \> 4\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

This deal appeared in a game agaist England who got vicyory two yeats ago.
Contract and bidding are same in both teams.

At one table opening lead is \c 6 followed by \c 3, \c 10 and \c A.
South succeeded trump finesse with \s J dropping 10. He doubted east has
\s 9. South led \d 3 to \d K. Ace won. West attacked a diamond by \d J.
South won in hand \d Q. South led \s Q follwed by \s K and \s A:
East shew out. Dummy's \h A was ruffed by west. A diamond trick defeated
contract.

At another table, opening lead \d A gave two winners to declarer:
contract was made giving a big swing againt strong England.

%-------------71------------------
\section {ace of trump can win anytime keeping control}
\qquad 2006/11/25 Kakagawa Governer Cup \#19
\begin{quote}
\crdima{S/vul:N-S}{%
  \begin{minipage}[t]{\br}
     5\s \\OL:\d A
  \end{minipage}}%
  {\hand{K97}{9852}{-}{AK9875}}%
  {\hand{AJ6}{3}{AK1073}{J643}}
  {\hand{84}{K10764}{J9864}{10}}%
  {\hand{Q10532}{AQJ}{Q52}{Q2}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\s \\
2\d  \> 3\c \> 5\d \> P \\
P  \> 5\s \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}

I thought my 5\d will be doubled surely. But north is
fighting in 5\s for higher rank seat in last round of
Swiss tournament.

Opening lead is \d A (\d K requests partner to show 
count.) South ruffed \d A by dummy. He led \s K from 
dummy. West won with ace at once and entered a long thinking.
He was too late. Before you win  and get a lead, you should decide
the next card to be led.

After all west led sigleton heart. South won. A diamond was
ruffed. He came back with \c Q carefully. Cashed \s Q collecting
east's trump. Then solid club are availabe to discard two diamond
loosers. 5 spape is made.

If west ducked \s K , west has the contol of trump.
South can not discard diamonds. 

The controle of trump determined the fortune.

Eddie Kantar said; The trump control is the name of the game.




%-----------------------72-----------------

\vspace{0.5cm}

In next deal west came up with a idea there is a sigleton king.
His idea  was not logical but simoe excuse.\\

\qquad 2005/2/26 Naitoh Cup \#13
\begin{quote}
\crdima{N/vul:Both}{%
  \begin{minipage}[t]{\br}
     3NT \\OL:\d A
  \end{minipage}}%
  {\hand{KQ954}{K654}{83}{A9}}%
  {\hand{87}{Q1082}{AQJ107}{64}}
  {\hand{A632}{A97}{J965}{753}}%
  {\hand{J10}{J3}{K42}{KQJ1032}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> 1\s  \> P \> 2\c \\
P \> 2\h \> P \> 3NT \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

After cashing \d A , west continued \d . South held up.
When east get a lead , E-W communication is interrupted.
West's diamonds were dead.

Eest heard the bidding well. He dreamed to be a heroin 
by punishing declarer's singleton king. Recently INT 
opner has a singleton king in minor suit sometimes.
If he understans the importance of entry and control,
he would not play the ace.

If he led \d Q along basic attack, he was promised to
take four winners in diamond. Contract is easily defeated.
 

%-----------------------73-----------------
\vspace{0.5cm}

\qquad 2007/11/16 WBG trial  \#11
\begin{quote}
\crdima{S/vul:none}{%
  \begin{minipage}[t]{\br}
     4\s \\OL:\c K
  \end{minipage}}%
  {\hand{10852}{A3}{83}{98642}}%
  {\hand{97}{642}{Q10654}{AKQ}}%
  {\hand{643}{J1085}{K972}{J10}}%
  {\hand{AKQJ}{KQ97}{AJ}{753}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 2NT \\
P \> 3\c \> P \> 3\h \\
P \> 3NT \> P \> 4\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead of king requests his parter to show the count of
the suit in any level. East plaed \c J. West shifted to diamond.
East's jack seems doubleton, therefore three tricks in club 
are sure. Another cashing club helps declarer's task.
Shiht to diamond is natural for the player who is challenging
at the trial game. South won with ace and drew trumo once.
He  cashed \h A and \h K. East followed \h 8 and \h 10 ,consealing 
\h 5. South made a mistake by drawing second round of trump.
He thought the drawing for safty play but it was 
fatal. If \h Q can not cashed , contract would never make,
So his safety is illusion. If he discards a diamond under the
\h Q , he has an ahead to establish dummy's club.

Good defense gets fine result.

There is an advise that attacking an ace from Axx against 
opponent's long suit is a loss of tempo.
Attacking your long suit is basic.
%-----------------------74-----------------
\vspace{0.5cm}

\qquad 2004/7/30 Montalt Cup   \#1
\begin{quote}
\crdima{S/vul:none}{%
  \begin{minipage}[t]{\br}
     3NT \\OL:\c K
  \end{minipage}}%
  {\hand{AJ8}{KJ6}{K1083}{762}}%
  {\hand{10972}{Q97}{Q74}{AKQ}}%
  {\hand{653}{8543}{J52}{984}}%
  {\hand{KQ4}{A102}{A96}{J1053}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\c \\
P \> 1\d \> P \> 1NT \\
P \> 3NT \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Since west doubted south's consealed major(
At 1NT there is no alert about south's four card
major.), he decideed to look at dummy by \c K.
It is a sad habit. At second trick west shifted to
spade. He was late on establishing race.
His \c K lost a tempo.

Let's continue the race. South wins \s Q and leads club.
Repeat again. When south estavlises fourth club. he has a
time to lose a diamond into east in order to increase a
winner.

If opening lead starts in spade, west can take four tricks in 
black suits. So south must guess the location of \h Q correctly.

\vspace{0.5cm}
{\bf closing intermission}\\


If solid three tops are in major suit,such as\\
Q74 , AKQ, 10972, Q72\\
\h K in openg lead is one of the choice.
In other word ,  3NT may be depened upon long minor suit .
Hear the bidding carefull


%-----------------------75-----------------
\section{rescue your partner not to being 
squeeze}

\qquad 2007/6/8 Yotsuya league  \#28
\begin{quote}
\crdima{S/vul:N-S}{%
  \begin{minipage}[t]{\br}
     3NT \\OL:\s 2
  \end{minipage}}%
  {\hand{109}{A4}{A108752}{K53}}%
  {\hand{K432}{862}{64}{A1098}}%
  {\hand{QJ87}{J973}{QJ9}{72}}%
  {\hand{A65}{KQ105}{K3}{QJ64}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1NT \\
P \> 3NT \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

South ducks opening lead twice,and leads \c 4
from hand followed \c 8, \c K and \c 7.
Another club from dummy follows \c 2 and \c Q.
How does west do? 

South did not tested run of diamonds. That inplies
he does not have both king and queen. He has some
honors in heart. So west ducks smoothly.

Declarer will aim either club 3-3 break or 
fourth trick in heart,

Most miserable sequence is below:
West wins \c A over \c Q. Cash a spade winner.
Since environment for squeeze has completed, 
rectifying loser count.
 Any lead 
from west goes to automatic squeeze againt east.

If west ducks,south must guess the difficult choice.



\vspace{0.5cm}

%-----------------------76----------------
\vspace{0.5cm}
{\bf mission impossible end play}\\

\qquad 2007/8/29 Yokohama sectional   \#11
\begin{quote}
\crdima{S/vul:none}{%
  \begin{minipage}[t]{\br}
     6\s X \\OL:\d A
  \end{minipage}}%
  {\hand{AQ9874}{KQ106}{-}{J75}}%
  {\hand{32}{AJ762}{AK542}{6}}%
  {\hand{-}{94}{QJ9763}{K10942}}%
  {\hand{KQ1065}{53}{108}{AQ83}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 2\s \\
3\s  \> 4\s \> 4NT  \> P \\
5\d  \> 5\s  \> 6\d \> P \\
P \> 6\s \> P  \> P \\
Dbl \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\



West's 3\s  was explaned that it invites to 3NT if spade is stopped.
(later 3\s was intended as Michaels Cue Bid\footnote{
Michaels is a cue-bid that promises a two-suited hand, with at least five cards in each suit. There is no point minimum for making a Michaels overcall, although obvious factors like vulnerability should be considered. Some partnerships also agree to specific ranges.
}.)
4NT is takeout.


South ruffed the openind lead by dummy.
He drew trumps twice.a small heart from hand.  West won at once.West retured 
\c 6. If west's club is singleton 8 or 10, south counted 3 tricks in club,
But he gave up the three tricks. South perfomed heart finess by 10.

In postmotem east asked west to took ace in secound round.
Once duck against KQ10x is natural whoever ace has. But in this deal
ducking does not succeed.



The declarer's winning sequence is below:
If west do not take at first, dummy's king wins. South comes back by \c Q.
South ruffs \d 10 by dummy, Come back again by \c A ,  lead a 
heart from hand. 


West takes with ace. West has no safty card to exit.


