\chapter{count}
Count is a basic principle of defense. It gives you
to estimate the hand. If you have the custom to count,
such as HCP ,shape and number of tricks, your defense will
promote.
\begin{itemize}
\item{declarer's HCP}
\item{declarer's pattern}
\item{number of declarer's trick}
\end{itemize}
In real game one of these item is not enough.
Several counts are required. Don't be troublesome for
counts.

\section{three basic counts}

(1)High Card Point\\

\qquad 2007/10/27 Yokohama BC cup \#20
\begin{quote}
\crdima{S/N-S}{%
  \begin{minipage}[t]{\br}
     4\h\\OL:\d J
  \end{minipage}}%
  {\hand{103}{K9754}{Q75}{Q107}}%
  {\hand{K4}{A1083}{J1064}{953}}%
  {\hand{Q987652}{Q}{K82}{J6}}%
  {\hand{AJ}{J62}{A93}{AK842}}%
  \end{quote}
\begin{quote}
\begin{bidding}
--  \> -- \> -- \> 1NT \\
P \> 2\d \> P \> 2\h \\
P \> 2NT \>  P \>  4\h \\
a.p.
\end{bidding}
\end{quote}
%
{\bf Remarks}\\
West led \d J, covered by queen ,king and ace. South
led a small heart to king dropping queen from west.  Return to south by \c A.
South led another small trump which west won by ten. East discarded \s 2.

Now the time is critical. Which card should he select? He abandoned spade attack by partter's negative \s 2. He reached that the only hope is \d 9 in west.
So he played \d 10 and \d 4. Unfortunatele south won and run clubs makeing 
contract. Instead of club run he can also make conract by drawing trump.

After the game, postmortem starts on \s2.
East could tell doubleton club by \c J but meaningless. Why east could not
play a card other than \s 2?

Another idea was that West should count south's high card point. At this point
south showed \d A \c A \c K and \h J totally  12 points. So both ace and queen 
of spade never in his hand.
1NT open\footnote{15 to 17 points} denies that  south has both ace and queen of spade .


When west won \h 10 ,he could switch to play \s K.
West shoud confess that fact before he accuses his partner,

\vspace{0.5cm}


(2){shape count}\\

\qquad 2005/2/9 NEC cup \#1
\begin{quote}
\crdima{N/None}{%
  \begin{minipage}[t]{\br}
     contract:4\h X\\OL:\s2
  \end{minipage}}%
 {\hand{A9}{32}{AJ432}{AKQ7}}%
  {\hand{J102}{QJ1065}{KQ87}{5}}%
  {\hand{Q8754}{A}{106}{109852}}%
  {\hand{K63}{K9874}{95}{J43}}%
   \end{quote}
\begin{quote}
\begin{bidding}
- \> 1\d  \> 1\s \> 2\h\\
P \> 4\h \> P \> P \\
Dbl \>  a.p.\\
\end{bidding}
\end{quote}
{\bf Remarks}\\

West's openg lead is \s 2.
Declarer took \s A \s K and ruffed last spade,
Small club to \c J and lead a club which was ruffed by west.
West led \d K. Dummuy's ace won. Third round of club was ruffed again.

At this time west,without consideration , led \h Q believing as a safe lead.
Actually east's ace won resulting only two down.

West should have count south's hand pattern as 3-5-2-3. So east 
must have a trump. If it was ace or nine , diamond's ruff get a 
gain in result. Anyway west should retuen diamond.
Lack of concentration ignored counting. Get in the habit of
counting.

\vspace{0.5cm}
%-------------------10---------------
(3){tricks for defeat}\\
\qquad 2004/9/30 Yoyohama sectional \#15
\begin{quote}
\crdima{W/E-W}{%
  \begin{minipage}[t]{\br}
     4\s \\OL:\d 6
  \end{minipage}}%
  {\hand{10}{94}{QJ942}{108532}}%
  {\hand{874}{A10532}{6}{J976}}%
  {\hand{965}{KQ876}{A87}{KQ}}%
  {\hand{AKQJ32}{J}{K1053}{A4}}%
  \end{quote}
\begin{quote}
\begin{bidding}
P \> P \> 1\h \> Dbl \\
4\h \> P \> P \> 4\s \\
 a.p.
\end{bidding}
\end{quote}
\begin{quote}
another table
\begin{bidding}
P \> P \> 1\h \> Dbl \\
4\h \> 4NT \> P \> 5\d \\
5\h \> 6\d \> Dbl \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Honorable mentions to be awarded to two
east players if they play best.

In our table, west led \d 6 as an opening lead.
East won with ace and retured \d 8. West ruffed.
He was temp to cash his \d A but realized that
it was the last trick. In order to ruff again he led
\h 10 hoping \h K in east.East returned \d and west succeeded
to ruff. Wonderful defense was by veteran madonna in east.

In another table, first four call were same as those of ours.
North's 4NT showed both monor suit. Final contract was 6\d  doubled.
Opening lead was \h A .West played \h 6. 
If east notices the discourage signal,
he could find club shift. Contract would be off two.
Actually Contract was off one.

Analyze the bidding and detect the signal for good defense.
%----------------11-------------------
\section{Both defenders lost chance}
\qquad 2005/4/2 Yanagiya cup \#24
\begin{quote}
\crdima{S/None}{%
  \begin{minipage}[t]{\br}
     3NT\\OL:\c 5
  \end{minipage}}%
  {\hand{Q973}{75}{1054}{AKQ10}}%
  {\hand{KJ10}{A103}{A76}{J865}}%
  {\hand{852}{J8642}{Q9}{973}}%
  {\hand{A64}{KQ8}{KJ832}{42}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> - \> 1\d \\
P \> 1\s \>P \> 1NT \\
P \> 2NT \> P \> 3NT \\
 a.p.
\end{bidding}
 \end{quote}
{\bf Remarks}\\

West leads \s 4 . North wins with ace.
Dummy's \d 10 was covered by west's queen according to the saying "
"Cover an honour with an honour"(10 is an honour) .
South's king won, East could duck easily because he noticed \d J in south.
South led \d 2 hoping east will play ace. But east won with \d 9 and led
\h 4 .south \h Q, west won by \h A. West led \h 10 . East small. 
Declare hold it. West's another heart resulted just-made:

\index{Merrimac coup}
A chance is occured in east. He overtakes \h J and shifts to spade,
Anothe chance is in west. After he gains lead with \h 10, \s K was killg lead.
It is called as
Merrimac coup{\footnote{Merrimac coup first
 arose in the deal of 1979 
world championship.Old player night never hear. Wikipedia tells:
The Merrimac coup (also known as Hobson's coup or Hobson's choice) is a contract bridge coup where a player (usually a defender) sacrifices a high card in order to eliminate a vital entry from an opponent's hand (usually a dummy). It was named after American steam ship Merrimac, which was sunk during the Spanish?American War in 1898 in Santiago de Cuba in an attempt to bottle up the Spanish fleet.}.
%
\section{partner's HCP}
\qquad 2004/2/3 Pucifico \#25
\begin{quote}
\crdima{E/E-W}{%
  \begin{minipage}[t]{\br}
     4NT\\OL:\s J
  \end{minipage}}%
  {\hand{9872}{A10842}{AJ6}{Q}}%
  {\hand{J1053}{QJ93}{2}{!0832}}%
  {\hand{K64}{765}{K1075}{AJ5}}%
  {\hand{AQ}{K}{Q9843}{K9764}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> 1\d  \> 2\c \\
P \> 2\h \>P \> 2NT \\
P \> 3NT \>a.p. \\
 
\end{bidding}
 \end{quote}
{\bf Remarks}\\

Openg lead is \s 3. At second trick south led \d 3 and 
took finesse with \d J.

In another table east won immedeately , so contract is made easily.
In our table east ducked  correctly. Dummy led \c Q. East ducked again.
Cash \d A and \d 6 to east's king. West was in trouble to discard. 
East retured spade, South cashed forth and fifth diamond.
As west sluffed a club and three heart , dummy did overtake with \h A and took 
remaining hearts .
This is due to west was believed his club was important.

Two fact was told to blame west. One is he negleced partner did open.
Another is he did not realized there are a few communication between north 
and south.
%-------------------------14---------------------------
\section{doubleton signal}
\qquad 2006/11/18 Koezuka cup \#3
\begin{quote}
\crdima{S/vul;E-W}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{J1087}{J1098}{A9}{AK7}}%
  {\hand{K9}{Q6}{KQ7632}{QJ10}}%
  {\hand{5}{A754}{84}{986432}}%
  {\hand{AQ6432}{K32}{J106}{5}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \>- \> - \> 2\s   \\
3\d  \> 4\s \>a.p. \\
 
\end{bidding}
 \end{quote}
{\bf Remarks}\\

Against \d K opening lead north won with ace.
Ease followed with \d 4 neglectng to put doubleton
signal.
Second trick is spade finesse. West won with \s K and
shifted to \c Q. Dummy won. After drawing last spade,
declare sluffed  \h 2 under \c K. Then dummy lead \d 9
to west \d Q  while east followed \d 8.

At this point east made a mistake by returning heart,
Following is his excuse.
Since west did not put a doubleton signal( high and low).
declare has no diamond now.
East excused that his trump was too  useless for the signal.

Anyway there is a definitive fact that if deaclarer has
doubleton diamond ,he must have sluffed a diamond in stead
of heart at trick five,

If west did not lead a heart, it remains for declarer to guess a
heart position,  If wrong, another table ends one down,



\section{recognize opponent's system}
\qquad 2000/9/22 princess Takamatsu \#10
\begin{quote}
\crdima{S/vel:Both}{%
  \begin{minipage}[t]{\br}
     4\s\\OL:\d K
  \end{minipage}}%
  {\hand{1032}{QJ54}{5}{AK1043}}%
  {\hand{AQ765}{K873}{K74}{Q}}%
  {\hand{98}{96}{QJ10982}{J97}}%
  {\hand{KJ4}{A102}{A63}{8652}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> -\> 1\d   \\
1\s \> 2\c \>P \> 2NT \\
P \> 3NT \>a.p. \\
 
\end{bidding}
1\d blue club
 \end{quote}
{\bf Remarks}\\

Opening lead is \s 6 followed by \s2 ,\s 4 and \s J. South led a
club. West played \c Q quickly, Declarer ducked as 
a typical avoidance play.
(\c Q might be a deceptive play pretending as a singleton,)

Question is which card should west return ? There are two choices.
Since south uses blue club system. he has never four cards of spade.
So \s A and another will  defeat contract,

Anothe choice is \d K  which is induced from the fact 2NT announced 
at most 12 HCP. So south denies both \d A and \d Q .

At the case of \d K contract is off two.

\section{second hand low}% section 1.8
%-------------------16-----------------
\qquad 2006/7/7 Studio \#2
\begin{quote}
\crdima{S/vul:E-W}{%
  \begin{minipage}[t]{\br}
     4\s\\OL:\s 6
  \end{minipage}}%
  {\hand{32}{KQ83}{Q98654}{J}}%
  {\hand{1086}{A952}{A7}{KQ105}}%
  {\hand{KJ}{J764}{J1032}{862}}%
  {\hand{AQ9754}{10}{K}{A9743}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> -\> 1\s   \\
P \> 1NT \> P \> 2\c \\
P \> 2\s \> P \> 4\s \\  
a.p. \\
\end{bidding}
 \end{quote}
{\bf Remarks}\\

This deal appeared in IMP game.
After analizing the bidding well, west led a trump
according to the standard policy. South won and led 
\d K. West won with ace . \index{odd-even signal}
East played \d 3 (if we use odd-even signal \footnote{Odd/Even Discards  are a type of signal for attitude and suit preference. 
The first discard of a spot card has the following meanings:
An odd spot card (9, 7, 5, 3) encourages that suit.
A high even spot card discourages that suit, and is a suit-preference signal for the higher side suit.
A low even spot card discourages that suit, and is a suit-preference signal for the lower side suit.
} \d 10 means even.
)
East led a trump  again. South led \h 10. Should west
take it with ace or not?

As cards lie,dummy has no entry. So if east take it with ace,
contract might be 3 down.
But if south happens to have doubleton heart ,this play allows three red
tricks in dummy.

Let's count the declarer's trick when east ducked. Only two
red tricks in dummy were not enough to make contact.

In IMP game such a sure defense is complimented.



%--------------------17----------------
Following is the example of safty defense\\
\qquad 2005/3/18 Ohfuna principal cup 
\begin{quote}
\crdima{N/None}{%
  \begin{minipage}[t]{\br}
     4\s\\OL:\c A
  \end{minipage}}%
  {\hand{AKx}{x}{AKQ9xx}{xxx}}%
  {\hand{x}{Qxx}{10x}{AKQJxxx}}%
  {\hand{Qxx}{AK10xxx}{Jxxx}{-}}%
  {\hand{Jxxxxx}{xxx}{x}{10xx}}%
\end{quote}
\begin{quote}
\begin{bidding}
3NT  \> Dbl \> P \> 4\s   \\
P \> P \>Dbl \> a.p. \\
\end{bidding}
 \end{quote}
{\bf Remarks}\\

\index{swiss team}
This deal appeared in swiss teams\footnote{
For many years Swiss Teams has been the most popular form of team event, but in recent years it has been overtaken by Knockout Teams. A Swiss Teams event is a partial Round-robin setup in such a way that winners play winners and losers play losers. It is based on the Swiss concept that governs play in most chess tournaments.
After each round, the game directors sort the team records and set up new matches between teams of approximately equal records. In general, teams are not permitted to play against each other more than once.} match. 
The bidding started with gambling 3NT which consist of solid  7 or 8 minor suit.East doubled . Finally east doubled south's 4 \s.

West cashed \c A . East began a signal with \h 10. West cashed \c K.
East comlpleted his signal with \h x, South played \c 10 as deceptive play.

At third trick west led \c Q despite of heart's encourage,
West became anxious about south's ruff. He found sure defense by ruffing
 it with queen, even if west had 8 club suit, \h A broke the contract.

After this game east apologized he should trust his partner. If partner had
8 clubs , he never lead \c Q. 

It is an usual custom that when gambling 3NT is doubled, west bids 4\c.

%---------------18--------------------
Following deal shows challenging defense.

\begin{quote}
\qquad 2005/3/19  Ohfuna principal cup \#1
\crdima{S/vul:None}{%
  \begin{minipage}[t]{\br}
     4\s\\OL:\d Q
  \end{minipage}}%
  {\hand{92}{AK109}{752}{AJ64}}%
  {\hand{K84}{875}{QJ93}{Q92}}%
  {\hand{107}{Q63}{A1086}{K1053}}%
  {\hand{AQJ653}{J42}{K4}{87}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> - \> 1\s   \\
P \> 2\c  \> P \> 2\s  \\
P \> 4\s \> a.p.
\end{bidding}
 \end{quote}

2\s guarentees 6  cards,

{\bf Remarks}\\

North-south has four losers in each suit,
The forcus is a establishing race between both sides
,\h 9 or \d 3.

Opening lead is \d Q. East wom with ace and returned original
fourth best \\d 6. South's king won. West played \d 3.

Souh les \h 2 and took finess with \h 10 .
When east won with \h Q, he is in a worry which card to be returned.
He realized one club trick is necessary beside of trunp trick.
Although dummy's \c A and \c J gave pressure for east to lead club,
he hurried to lead club. Otherwise suouth would discard a club under
the heart.

When west won a trump , \c K broke the contact.

Let's think the case declarer took tump finesse first 
before heart finesse, West has a worry to the return,
He knew south  bas no diamond because east have told 4 cards;
He was not convinced club return is correct,

In order to remove his worry, he can duck trump finesse.
South will trasfer to dummy by heart and will attemp trump
finesse. When east wins with \s K ,
he finds club return without hesitation.

West must be careful for club attack.
Returning \c K fails. Against small club , dummy will play 9.
East wins with \c 10 and returns small to west' king.
Dummy will hold unwillingly, Here west acomplishes defense by
switching to spade,


\section{various situation}  % section 1.9
%------------20-----------------------

\qquad 2007/2/27 Yotsuya league \#10
\begin{quote}
\crdima{W/vul:Both}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{K82}{106}{104}{AJ9832}}%
  {\hand{J1096}{A943}{K6}{K84}}%
  {\hand{Q5}{852}{9732}{Q1075}}%
  {\hand{A743}{KQJ7}{AQJ85}{-}}%
\end{quote}
\begin{quote}
\begin{bidding}
P \> P \> P \> 1\d  \\
Dbl \> 2\c \> P \> 3NT \\
a.p.
\end{bidding}
 \end{quote}

{\bf Remarks}\\

Opening lead is \s 3.
East won with \s K. As he thought spade attack seems passive defense,
As he imaged west' \c K , he shifted to \c 3, In real game, declarer's
poor play and went to 2 down. This defense is dengerous. His idea was 
reckless. Declare might make contract.
 
}


%-------------21----------------------
Next deal shows defender's dramatic desision, It must
be played smoothly.

\qquad 2005/8/6 Yokohama mayor cup \#14
\begin{quote}
\crdima{S/vul:None}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{A9}{J32}{Q8732}{J97}}%
  {\hand{J6532}{A1096}{9654}{-}}%
  {\hand{K84}{Q74}{KJ}{G19432}}%
  {\hand{Q107}{K85}{A10}{AK865}}%
\end{quote}
\begin{quote}
\begin{bidding}
P \> P \> P \> 1\d  \\
Dbl \> 2\c \> P \> 3NT \\
a.p.
\end{bidding}
 \end{quote}
{\bf Remarks}\\
Opening lead is \h 3. North \h7 . East \h10 . South won with ace.
South led \s 10 immedeately. West cover it with \s Q without
hesitation. North ducked after a little thinking. West led \h Q.
North \h 9 , east \h 2. Although west hesitated, he continued heart,
Declarer cashed four diamond tricks.East discarded two samll club
smoothly. Finally south tried to finesse spade. he was deceived by east.

If east protected both kings, the poition became below:
\begin{quote}
\crdima{N/None}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{AJ7}{-}{-}{A3}}%
  {\hand{82}{-}{-}{J94}}%
  {\hand{K9}{J}{-}{K8}}%
  {\hand{5}{-}{-}{Q107}}%
\end{quote}%

South can estimate the east has both black kings.
It is not so  difficult to play thow-in to east.

In next deal west did not corporated.
\vspace {0.5cm}

%------------------23------------------------
\qquad 2007/2/13 Yokohama cup \#30
\begin{quote}
\crdima{N/None}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{KQJ942}{J853}{J}{104}}%
  {\hand{1075}{A7}{K74}{QJ962}}%
  {\hand{83}{10962}{10852}{K53}}%
  {\hand{A6}{KQ4}{AQ632}{A87}}%
\end{quote}
\begin{quote}
\begin{bidding}
P \> 2\s  \> P \> 2NT  \\
P \> 3\s \> P \> 3NT \\
a.p.
\end{bidding}
 \end{quote}
{\bf Remarks}\\

South ducked twice on the club lead. East's card was
\c 5 \c K  then \c 3. After winning with \c A , six cards of spade 
cashed, South had two ways of line  sucha as  diamond finess and
throwing into west, In generally a defender should decide 
remaining cards in advance.

West has decide to leave \d K alone, But since west discarded all diamond,
the game was over by running diamond.

Even if west protected \d K, south woulf find throw-in end play.

Anyway east should keep at least one diamond.

Next deal shows false card played smoothly.
%--------------24----------------
\vspace{0.5cm}
\qquad 2007/9/15 Takamatu cup \#7
\begin{quote}
\crdima{S/vul:Both}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{Jxx}{x}{xxx}{AQxxxx}}%
  {\hand{}{A7}{Jxxx}{}{}}%
  {\hand{}{AKxxx}{}{}}%
  {\hand{Kxx}{Q10x}{AKx}{KJxx}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> -\> 1NT  \\
P \> 3\c \> P \> 3NT \\
a.p.
\end{bidding}
 \end{quote}
{\bf Remarks}\\
North's 3\c is forcing to game. As south convinced all
suits stopped,he bids 3NT without hesitation.

Opening lead looks like fourth best of heart.
East played \d A immedeately( not \h K) and returned
a small heart (like fourth best).

South played 10 and west jack won. Heart attack defeated
contract.

South was comletely uncapped. At another table contract
is 3\c , 8 IMP behind.
East told that when a strong player was deceided, he
feeled wonderful.

Another resemble example:
At IMP game last four cards are below.\\
\qquad \qquad \d A964\\
\qquad \d 1087 \qquad \d KQ\\
\qquad \qquad \d J53\\

Declare led \d 4 from dummy. East played \d Q honestly.
When south gets a lead he has to guess correctly.Whether east has 
\d K or \d 10.

\index{intra-finesse}
A declare cashed \d A dropping king. Another
declare took intra-finesse\footnote{
Finesses which involve a second-round drop or pin are sometimes referred to as "intra-finesses".}by jack.

%-----------------25----------------------
%Nest deal indicates mission impossible.
 .
\vspace {0.5cm}

{\bf mission impossible "Morton's fork coup"}\\

\qquad 2007/3/16 Ohfuna principal cup
\begin{quote}
\crdima{S/None}{%
  \begin{minipage}[t]{\br}
     5\h\\OL:\s K
  \end{minipage}}%
  {\hand{A10x}{Q9x}{Jx}{KQJxx}}%
  {\hand{KQxxx}{xx}{Kx}{Axxx}}
  {\hand{Jxxxx}{Ax}{xxxx}{xx}}%
  {\hand{-}{KJ10xxx}{AQxxx}{xx}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\h  \\
1\s  \> 2\s \> 4\s \> 5\d\\
P \> 5\h \> a.p.
\end{bidding}
 \end{quote}

{\bf Remarks}\\

Opening lead \s K.
South has inevitable losers \c A and \h A.

A pitiful declarer won with ace and led a trump.
West went up immedeately and returned diamond.

\index{Morton's fork coup}
A nice deaclarer has more favarite line.
He ruffed spade by hand and led a small club.
This club lead is called Morton's fork coup,
\footnote{
A Morton's fork is a type of false dilemma in which contradictory 
observations lead to the same conclusion. It is said to have originated
with the rationalising of a benevolence by the 15th century
 English prelate John Morton.
Morton's fork coup is a coup in contract bridge that forces an opponent 
to choose between:\\
letting declarer establish extra tricks in the suit led; or\\
losing the opportunity to win any trick in the suit led.\\
It takes its name from the expression Morton's fork.}
West is in dilemma.
Unless west plays ace . dummy's \s A is useful to 
discard a club. So west won at once , South has enough winners
to make contract.

To trump at first rick allows south to decide discarding card under 
\s A later. Such a play is called as Morton's fork coup.
%---------------------------27-------------------------------------

