Since the era of whist, a defender tempted to attack
his long suit if he had many trump cards. Four trumps are
enough to attack his suit. Such a hand contains a short suit,
singleton or doubleton, So you must compare  your 
attack between long suit and short suit. The ultimate selection depends upon
your luckness. Let's study the forcing defense.


\section{forcing defense}
%----------------------page 146-------------------
\qquad 2007/10/27 Yokohama BC cup \#14
\begin{quote}
\crdima{W/None}{%
  \begin{minipage}[t]{\br}
     5\h X \\OL:\d 3
  \end{minipage}}%
  {\hand{1063}{1073}{AJ}{AK1086}}%
  {\hand{Q9874}{5}{K10863}{73}}
  {\hand{A2}{A942}{Q9754}{J4}}%
  {\hand{KJ5}{KQJ87}{2}{Q952}}%
\end{quote}
\begin{quote}
\begin{bidding}
P  \> 1\c \> 1\d  \> 1\h \\
1\s \> Dbl \> P \> 4\h \\
5\d \> P \> P  \> 5\h \\
P \> Dbl \>a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

South wins the opening lead with dummy's ace. He drew trumps,
At the third round east wins with ace. He did not want south discrds a
spade under the dummy's club. east played \s A and a spade. Contract
was doublely made. East should leaf diamond, South was forced to trump.
If he drew all, game is in no trump. Although south can cash 5 clubs, 
he can not get a sapde. When east wins with \s A, his diamonds defeats
contract.
\vspace{0.5cm}

Next deal also shows forcing defense.\\
%----------------------page 147-------------------
\qquad 2007/2/21 Yokohama Cup \#18

\begin{quote}
\crdima{N/None}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{AK74}{K52}{J84}{J72}}%
  {\hand{8532}{AQ84}{A107}{A6}}
  {\hand{QJ109}{9}{K53}{109854}}%
  {\hand{6}{J10763}{Q982}{KQ3}}%
\end{quote}
\begin{quote}
\begin{bidding}
1\d \> P \> 1\s  \> P \\
2\s \> P \> P \> 3\h \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

A young pro-player bid 3\h  bravely  at a ballancing
position. Opening leader west was tempted to take \c A 
in oder to look at dummy, But he has trump control with
four trumps and ace. Straightforward methode is a spade,
Because they have at least 8 cards.

Against spade lead dummy wins with ace, \h 2 from dummy.
West wins \h J with \h Q. He leads another spade, Dummy
wins with king and leads trump. West wins \h 10 with \h A.
West leads a trump to king. South leads club to west's ace.
West drew trump with 8 and led spade, South lost control.
Contract went to three down.

\index{pump}
If south played \c A and ruffed a club, he might saved in two
down, To force opponent to ruff is called as  pump. This is
the basic of forcing defense.

\vspace{0.5cm}
%----------------------page 148-------------------
\qquad 2007/3/171 Ofuna President Cup \#7
\begin{quote}
\crdima{E/Bothh}{%
  \begin{minipage}[t]{\br}
     4\s \\ OL:\d A
  \end{minipage}}%
  {\hand{J1094}{QJ62}{7643}{3}}%
  {\hand{8632}{K}{AKJ8}{K1063}}
  {\hand{-}{107543}{Q102}{A8752}}%
  {\hand{AKQ75}{A97}{95}{Q94}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> P  \> 1\s \\
P \> 3\s \> P \> 4\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\
This 4\s\  is not paticular.
Esat encouraged opening lead \d A, West continued diamonds.
South ruffed third diamond. \s J told suuth bad break. From
dummy \c 3. East won with ace and led a club. Dummy ruffed.
A finess with \h Q failed to west's \h K. South ruffed west's \d J.
West had longer hearts  already. South drew trup, His \h A was
ruffed by west and counted all clubs, Three down.
Honest defense with long suit is not so difficult forcing defense.


\vspace{0.5cm}
%----------------------page 149-------------------
\qquad 2006/11/25 Kanagawa Governer Cup \#24
\begin{quote}
\crdima{S/Both}{%
  \begin{minipage}[t]{\br}
     4\s \\OL: \c 6
  \end{minipage}}%
  {\hand{J5432}{AQJ3}{J42}{7}}%
  {\hand{Q986}{9}{A53}{KJ864}}
  {\hand{A}{87642}{Q986}{1052}}%
  {\hand{K107}{K105}{K107}{AQ93}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> - \> -  \> 1NT \\
P \> 2\c \> P \> 2\d \\
P \> 2\h \> P \> 2\s \\
P \> 4\s \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

\index{Smolen convension}
After Stayman convention, N-S announced "Smolen\footnote{
After a 1NT opening, Smolen allows responder to show 5-4 or 4-5 shape in the majors with game-forcing values. One advantage is that the opening bidder always becomes declarer if a major-suit game is reached.
}" using.
West can estimate their hand pattern. As wesst has four
trumps, he refused sigleton heart. 
West led \c 6 as a forcing play. South wins with queen ,enters
to dummy with \h Q, leads a small spade. What does 
east ,winning with ace, do? He gave up to get club and
shifted to diamond, This was a unfavarable shift. Dummy's
jack won, He resumed to draw trumps with king and 10.
West won with queen and attacked club. But too late.
Declarer made contract.

At another table ,sigleton heart lead reached to
set down one. In our table east's diamond shift was
fatal. He should continue his partner's club.
\index{pump}

This shot recovered west's wrong openinng lead.
As dummy's trump is long the pumping play dose
not rise in east. The postmtem was difficult.

Your job is to folloow partner's defense unless you have an overriding reason no to do so.\\
\begin{flushright}{
Mike Lawrence}
\end{flushright}


\section{pumping dummy}
%----------------------page 151-------------------
\qquad 2005/6/29 yokohama sectional \#9
\begin{quote}
\crdima{S/E-W}{%
  \begin{minipage}[t]{\br}
     4\h \\OL:\c 7
  \end{minipage}}%
  {\hand{95}{J10984}{Q10862}{J8}}%
  {\hand{J8732}{5}{97}{76543}}
  {\hand{Q106}{AQ63}{K2}{K1092}}%
  {\hand{AK4}{K72}{AJ543}{AQ}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 2NT  \\
P \> 3\d \> P  \> 3\h \\
P \> 3NT \> P \> 4\h \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

In both table bidding,contract and opening lead were same. But
the results were different. At a table declarer ruffed spade in
dummy after cashing ace and king. Usually dummy's trump is shorter
than that of declare. It was his custom to use dummy's trum before
drawing.

South led \h J to finesse \h Q. East won with ace and led club,
South won with \c Q.
As dummy has no entry, south cashed \h K. He lost trump queen.
East's club attack succeeded going to down one.
Declarer shortened his long trump by himself as does suicide.

At another table, declarer led \h K from his hand.
If a defender has singleton queen, he can save trump 
in one loose. East won with \h A. He retured club. South
led trumo. East ducked. Lead was in dummy. South was wise to
take diamond finess before drawing trump.
South lost \h Q. He has a control againt club.

To keep trump controls is basic principle.

\vspace{0.5cm}

%----------------------page 152-------------------
\qquad 2004/9/30 yokohama sectional \#18

\begin{quote}
\crdima{N/E-W}{%
  \begin{minipage}[t]{\br}
     4\s\\OL:\c Q
  \end{minipage}}%
  {\hand{AQ65}{A832}{107}{K97}}%
  {\hand{4}{KQ9}{AJ65}{QJ832}}
  {\hand{9873}{J1065}{Q3}{1064}}%
  {\hand{KJ102}{74}{K9842}{A5}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> 1\c  \> - \> 1\s  \\
P \> 2\s \> P  \> 4\s \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

When you want to play forcing defense, a contract with 4-4 fit
is hardly attacked, Next deal shows a rare example.

At a table, opeining kead was \h K, Declarer once ducked, He won
next heart with \h A. From dummy \d 10 was led. Covered with \d Q ,
\d K amd \d A, West led a heart which was ruffed at hand, Second 
diamond was led and west east won with jack. At this time west has no heart.
He was  tempted to lead club. But he noticed too late because 
declarer will draw trmps and cash all diamonds, He imaged his partner's
hand with four trumps and doubleton diamond.

So west led a diamond. Dummy was forced to ruff. N-S could not draw 
draw trump. Nice defense be praised.

At the another table opening lead is \c Q. Dummy won with king. East
discarded \c 6 , south \c 5. From dummy \d 10, covered \d Q, \d K and \d A.
West cashed \d J and led \d 5. South ruffed it with \s Q and collected trumps.
By established diamnod south made contract. West's idea may be
considerable. But after they got three tricks, further attack was unknown.
Whole trick count is more respectable than easy-going defense.

The Straightforward method for this deal is forcing attack by west.
He led the longest suit at opening and cotinued at the third trick.
Moreover when west won with \d J, he led club. If south ruffed it,
careful play must be required for south against 4-1 trump break.

A comment should be added  that if south did not ruff the thir club
and discared a heart, he could make contract.

\vspace{0.5cm}

%----------------------page 154-------------------
\qquad 2004/9/30 yokohama sectional \#18
\begin{quote}
\crdima{S/E-W}{%
  \begin{minipage}[t]{\br}
     4\h \\OL: \d A / \h J
  \end{minipage}}%
  {\hand{-}{Q532}{Q862}{A7432}}%
  {\hand{63}{J1096}{AK94}{J65}}
  {\hand{AKQ1042}{7}{1075}{1098}}%
  {\hand{J9875}{AK84}{J3}{KQ}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\s  \\
P \> 1NT \> P  \> 2\h \\
P \> 3\h \> P \> 4\h \\
a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Biddings at both tables are same. Madonna sitting at west
led \d A without deep delibration. At glancing dummy she hurried to
shift to trump witn \h J.When she gota lead with \d A, she led
trump again. South made contract easily.

At another table, the famouse player with his curious playing
led \h J according to standard defense agaist cross-ruff.
As declarer believe 3-2 trump break, he lost contract.
West emphasized his trump lead at postmotem,

There remains a deeper analisys at trick three. When west won
\d A, professor sitting at east followed \d 10.

Since east did not put a doubleton signal, he must have
three cards. \d 10 is not sequential from bottom. It wsa a
signal for suit preference. If west shifted to spade, dummy's trump
is shorten. There remain a chance of defense. If south was free
against 4-1 trump break, he will fail his contract.
Remember there is such a defense,

An excellent south player might fight against 4-1 break
by cross-ruff. 4H can be make. 

\vspace{0.5cm}
%----------------------page 155-------------------
\qquad 2004/7/27 Montalt \#25
\begin{quote}
\crdima{N/None}{%
  \begin{minipage}[t]{\br}
     Play:\\demo
  \end{minipage}}%
  {\hand{10}{AKJ3}{Q97632}{A8}}%
  {\hand{54}{10865}{K105}{Q1072}}
  {\hand{QJ73}{Q942}{4}{K963}}%
  {\hand{AK9862}{7}{AJ8}{J54}}%
\end{quote}
\begin{quote}
\begin{bidding}
- \> -  \> - \> 1\s  \\
P \> 2\d \> P  \> 2\s \\
P \> 3\h \> P \> 3\s \\
P \> 4\s \> a.p.
\end{bidding}
\end{quote}
{\bf Remarks}\\

Opening lead is \c 2 followed by \c 8, \c K and \c 4.
East returned \c 3 after a little thinking. South won with \c A.
Dummy led \d 2, Finesse with jack failed, Here is an important
point but west led heart without loss. Sourh led trump 10 and
reduced the trump loosers. He made contract.

Usually east returns his sigleton diamond or trump. His \c 3
wanted to force to ruff a club in dummy. Therefore west's
\c thwarts declarer's trump finess.




