
A while ago, I published "Deeper, More Fun", but next time I try to write mainly on defense, and I occasionally continue to collect and research hands.



The OL of the suit contract is not the traditional 4th vest, but the 3rd low, and the signal is not the so-called standard, it seems to be mainstream among people above a certain level such as upside down signal etc. is. Not only for this, but there are mistakes between partners, which can lead to mistakes. Defense is usually considered and researched with a partner, but depending on the play of the declarer, there are many variations and it is often complicated. Compared to play, there are some things that are not always scientific, and the accumulation of reasoning and inferences is also important. In addition, when the post-mortem time is limited, there are cases in which sufficient studies cannot be conducted, resulting in consequential theory or not being noticed. With that in mind, I'm trying to analyze it in depth, but it's hard and complicated.




However, I don't think the basic form will change, so I sorted out the cuts and tried to make it easier to understand. There may be different opinions depending on the handling, but the defense first counts (in the extreme case, it starts and ends with the count), and then gives the correct signal at the timing when there is no misunderstanding between partners. Its interpretation. Finally, the idea of defense itself (in a sense, the accumulation of reasoning) is a flexible idea, for example, in Go, it is said to be "reason", but I wrote it in search of the ideal of sublimating to that level. Is


've summarized them in an easy-to-understand manner so that you can understand the essence of counting, communication, playing cards, forcing defense, etc. Along the way, signals, discards, etc. have been added, including reconfirmation of basic matters.


Under the influence of the corona virus, we released a limited electronic version once for the occasional time when we could not go out, and for the comfort of stay home week, but after that, we made considerable modifications and refined it, and finally we will draft this book. have become. I hope you enjoy it.



This is a sister magazine following the previous work, and a word instead of the introduction. As usual, everyone like Karahenki, Madonna, etc. loves bridges, but they are making efforts to improve, and there are some successful cases, but it seems that there are many cases where it does not go well. Focusing on those hands, it is said that there may be different defenses by inferring (inspired) from different thinking processes or different clues (inferences).
For those who want to gain more experience through actual b

attles and aim to improve their level, or those who are lamenting the decrease in the number of games these days, we hope that you will read it carefully, and it will be useful and enjoyable for accumulating experience. Then from Chapter 1.
\begin{flushright}
{2020.8.1 author Kataoka Hisami}
\end{flushright}


\vspace{1cm}
{\bf translator's comment}\\

Above sentences were traslated by AI app. program. It contains
qurious English. In order to show AI's power, I dare to leave them
as they were. LOI (Laugh Out Immeadiatly)

This book is written under the LaTex. Mr C.G. van der Laan opened
type set program for bridge, I must say gratitude for him.

All the footnotes were added by translator. It might be
helpful for old readers,
\begin{flushright}
{2020.12.25 Yoshikawa Takeshiro}
\end{flushright}

